---
#title: "Wine Quality Prediction Project"
#authors: "Autumn Heyman, Erin Weaver, Georgia Miller"
---
# File Setup Tasks
## Import Libraries

```{r}
library("tidyverse")
library("caret")
library("lmtest")
library("magrittr")
library("dplyr")
library("tidyr")
library("popbio")
library("e1071")
library("PerformanceAnalytics")
library("corrplot")
library("corpcor")
library("MASS")
```

## Set Working Directory
*** can be manually overridden by selecting source file location from the session menu **

```{r}
setwd("/Users/georg/Documents/GitHub/TheThreeMusketeers")
```

## Import Dataset

```{r}
wineqt <- read.csv("Data/WineQT.csv")
head(wineqt)
```

# Data Wrangling 

## Drop Id Column 

```{r}
wine_subset <- wineqt[, c(1,2,3,4,5,6,7,8,9,10,11,12)]
```



********* STOP SIGN ******** :)


# RUN THIS SECTION TO create ordinal model with 3 groups defined as 3-4, 5-6, 7-8


## Recode into three groups

```{r}

wine_subset$qualityR <- NA
wine_subset$qualityR [wine_subset$quality==3] <- 0
wine_subset$qualityR [wine_subset$quality==4] <- 0
wine_subset$qualityR [wine_subset$quality==5] <- 1
wine_subset$qualityR [wine_subset$quality==6] <- 1
wine_subset$qualityR [wine_subset$quality==7] <- 2
wine_subset$qualityR [wine_subset$quality==8] <- 2
head(wine_subset)

```
## Drop Quality

```{r}
wine_wrangled <- wine_subset[, c(1,2,3,4,5,6,7,8,9,10,11,13)]
head(wine_wrangled)
```


## Check All Data Types 

```{r}
str(wine_wrangled)
```


# Creating a Base Model  

## Define the Order of the Dependent Variable
```{r}

wine_wrangled$qualityR = factor(wine_wrangled$qualityR, levels = c("0", "1", "2"), ordered = TRUE) 

```

## Exploratory Analysis

### Summarizing the dataset
```{r}
summary(wine_wrangled)
```


## Dividing data into training and test set  *** REVIEW THIS SECTION**
*** how to determine appropriate sample size
*** what is seed and how to determine appropriate value

### Random sampling 
```{r}

samplesize = 0.60*nrow(wine_wrangled)
set.seed(100)
index = sample(seq_len(nrow(wine_wrangled)), size = samplesize)

```

### Creating training and test set 
```{r}
datatrain = wine_wrangled[index,]
datatest = wine_wrangled[-index,]
```

## Create the Ordinal Logistic Regression Model
```{r}

model= polr(qualityR ~ fixed.acidity + volatile.acidity + citric.acid + residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide + density + pH + sulphates + alcohol, data = wine_wrangled, Hess = TRUE)

summary(model)

```




********* STOP SIGN ******** :)
** Clean Environment, rerun setup tasks, and run the next section


# RUN THIS SECTION TO create an ordinal model with 3 groups defind as 5, 6, 7-8

## Subset the data to only observations with a Quality of 5 or More.
*** alternate path: recode entire data set into two groups

```{r}

#wine_wrangled <- wine_subset %>% filter(quality >=5)
#head(wine_wrangled)

```

## Recode to combine observations with Quality 7 & 8 
```{r}

#wine_wrangled$qualityR <- NA
#wine_wrangled$qualityR [wine_wrangled$quality==5] <- 0
#wine_wrangled$qualityR [wine_wrangled$quality==6] <- 1
#wine_wrangled$qualityR [wine_wrangled$quality==7] <- 2
#wine_wrangled$qualityR [wine_wrangled$quality==8] <- 2
#head(wine_wrangled)

```
## Drop Quality

```{r}
#wine_wrangled <- wine_subset[, c(1,2,3,4,5,6,7,8,9,10,11,13)]
#head(wine_wrangled)
```


## Check All Data Types 

```{r}
#str(wine_wrangled)
```


# Creating a Base Model  

## Define the Order of the Dependent Variable
```{r}

#wine_wrangled$qualityR = factor(wine_wrangled$qualityR, levels = c("0", "1", "2"), ordered = TRUE) 

```

## Exploratory Analysis

### Summarizing the dataset
```{r}
#summary(wine_wrangled)
```


## Dividing data into training and test set  *** REVIEW THIS SECTION**
*** how to determine appropriate sample size
*** what is seed and hot to determine appropriate seed value

### Random sampling 
```{r}

#samplesize = 0.60*nrow(wine_wrangled)
#set.seed(100)
#index = sample(seq_len(nrow(wine_wrangled)), size = samplesize)

```

### Creating training and test set 
```{r}
#datatrain = wine_wrangled[index,]
#datatest = wine_wrangled[-index,]
```

## Create the Ordinal Logistic Regression Model
```{r}

#model= polr(qualityR ~ fixed.acidity + volatile.acidity + citric.acid + residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide + density + pH + sulphates + alcohol, data = wine_wrangled, Hess = TRUE)

#summary(model)

```



********* STOP SIGN ******** :)
** Clean Environment, rerun setup tasks, and run the next section



## Creating a Confusion Matrix *** MODIFY TO FIT NEW ANALYSIS ***

```{r}
cmatrix <- caret::confusionMatrix(wineqt$PredictedR, wineqt$qualityR2)
cmatrix
```


# Assumption Testing:

## Assumption 1: The Dependent Variable is Ordered

## Assumption 2: One or more of the independent variables are either continuous, categorical, or ordinal

## Assumption 3: Absence of Multicollinearity

### Pearson's Test

```{r}
chart.Correlation(wine_subset, histogram=FALSE, method="pearson")
```

### Correlation Matrix
```{r}
corr_matrix <- cor(wine_subset)
corr_matrix
```

### What is This Called :)
```{r}
corrplot(corr_matrix, type="upper", order="hclust", p.mat = corr_matrix, sig.level = 0.01, insig="blank")
```

## Assumption #3: Absence of multicollinearity

```{r}
cor2pcor(cov(wine_subset))
cor2pcor(cov(wine_subset))
```

```{r}
winecor <- ginv(cor(wine_subset))
colnames(winecor) <- colnames(wine_subset)
rownames(winecor) <- colnames(wine_subset)
winecor
```

```{r}
corrplot(corr = winecor, method = "number", is.corr = FALSE)
```

## Assumption #4: Logit Linearity *** MODIFY TO FIT NEW ANALYSIS ***

```{r}
wine1 <- wineqt %>% dplyr::select_if(is.numeric)
predictors <- colnames(wine1)
wine1 <- wine1 %>% mutate(logit=log(probabilities/(1-probabilities))) %>%
gather(key= "predictors", value="predictor.value", -logit)
```

```{r}
ggplot(wine1, aes(logit, predictor.value))+
geom_point(size=.5, alpha=.5)+
geom_smooth(method= "loess")+
theme_bw()+
facet_wrap(~predictors, scales="free_y")
```

## Assumption #5: Absence of Influential Outliers *** MODIFY TO FIT NEW ANALYSIS ***

```{r}
infl <- influence.measures(mylogit)
summary(infl)
```
### Results indicate no evidence of **influential** outliers

Box Plot Method

### all box plots
```{r}
boxplot(wine1)
ggplot(stack(wine1), aes(x = ind, y = values))+
  geom_boxplot(fill='rosybrown', color="darkred") +
  coord_flip()
```

All variables have outliers.



*********************** MOVING FORWARD **************************

# Correcting for Violation of Assumptions

## Corrections for Violation of Multicollinearity

```{r}
```

## Corrections for Violation of Logit Linearity
```{r}
```


********************* PLACE HOLDER FOR OLD CODE BELOW HERE ***********************

### Convert the Recode Column to a Numeric Format xxxxx

To ensure that the data was continuous, I will covert the new quality column to s numeric column.
```{r}
wine$qualityR2 <- as.numeric(wine$qualityR)
head(wine)
```

### Subsetting Data
I will create a data frame with the numeric quality column and the independent variables.
```{r}
wine_subset <- wine[, c(1,2,3,4,5,6,7,8,9,10,11,16)]
```

## Testing for Multicollinearity

The VIFs for fixed acidity and density are greater than 5 and may be causing multicollinearity to be present in the data.

## Test for Independence of Errors

We are looking for pretty even distribution of points all the way across the x axis. 
We have that, so have met the assumption of independent errors.

### Perform Durbin-Watson Test to confirm results of intial test

Output:
Durbin-Watson test

data:  mylogit
DW = 1.8156, p-value = 0.001465
alternative hypothesis: true autocorrelation is not 0

Since DW value is within 1-3 range, we have met the assumption of independent errors. 



