---
title: "Wine Quality Prediction Project"
authors: "Autumn Heyman, Erin Weaver, Georgia Miller"
output: html_document
---
# File Setup Tasks
## Import Libraries

```{r}
library("tidyverse")
library("caret")
library("lmtest")
library("magrittr")
library("dplyr")
library("tidyr")
library("popbio")
library("e1071")
library("PerformanceAnalytics")
library("corrplot")
library("corpcor")
library("MASS")
library("brant")
```

## Set Working Directory
*** can be manually overridden by selecting source file location from the session menu **

```{r}
setwd("/Users/georg/Documents/GitHub/TheThreeMusketeers")
```

## Import Dataset

```{r}
wineqt <- read.csv("Data/WineQT.csv")
head(wineqt)
```

# Data Wrangling 

## Drop Id Column 

```{r}
wine_subset <- wineqt[, c(1,2,3,4,5,6,7,8,9,10,11,12)]
```

## Recode into three groups

```{r}

wine_subset$qualityR <- NA
wine_subset$qualityR [wine_subset$quality==3] <- 0
wine_subset$qualityR [wine_subset$quality==4] <- 0
wine_subset$qualityR [wine_subset$quality==5] <- 1
wine_subset$qualityR [wine_subset$quality==6] <- 1
wine_subset$qualityR [wine_subset$quality==7] <- 2
wine_subset$qualityR [wine_subset$quality==8] <- 2
head(wine_subset)

```
## Drop Quality

```{r}
wine_wrangled <- wine_subset[, c(1,2,3,4,5,6,7,8,9,10,11,13)]
head(wine_wrangled)
```

## Check All Data Types 

```{r}
str(wine_wrangled)
```


# Exploratory Analysis

### Summarizing the dataset
```{r}
summary(wine_wrangled)
```

********* STOP SIGN ******** :)

# Assumption Testing:

## Assumption 1: The Dependent Variable is Ordered
### Results of Test: Pass.

## Assumption 2: One or more of the independent variables are either continuous, categorical, or ordinal
### Results of Test: Pass.

## Assumption 3: Absence of Multicollinearity

### Correlation Matrix
```{r}
wine_wrangled$qualityR <- as.numeric(wine_wrangled$qualityR)
corr_matrix <- cor(wine_wrangled)
corr_matrix
```

### Results of Test:

### Correlation Plots

```{r}
corrplot(corr_matrix, type="upper", order="hclust", p.mat = corr_matrix, sig.level = 0.01, insig="blank")
```

```{r}
corrplot(corr_matrix, method = "number", is.corr = FALSE)
```

### Pearson's Test

```{r}
chart.Correlation(wine_wrangled, histogram=FALSE, method="pearson")
```

#### *** OLD CODE TO REVIEW ***

**** REVIEW *** what is this test? Independence of errors? ***
```{r}
cor2pcor(cov(wine_wrangled))
cor2pcor(cov(wine_wrangled))
```

*** what does giv() do in this section of code?  winecor does not equal corr_matrix
```{r}
winecor <- ginv(cor(wine_wrangled))
colnames(winecor) <- colnames(wine_wrangled)
rownames(winecor) <- colnames(wine_wrangled)
winecor
```

```{r}
corrplot(corr = winecor, method = "number", is.corr = FALSE)
```



## Assumption 4: Proportional Odds

```{r}
brant(model)
```

### Results of Test: Pass



## Assumption #4: Logit Linearity *** MODIFY TO FIT NEW ANALYSIS ***

### box tidwell goes here
```{r}

```

### what's this called
```{r}
wine1 <- wineqt %>% dplyr::select_if(is.numeric)
predictors <- colnames(wine1)
wine1 <- wine1 %>% mutate(logit=log(probabilities/(1-probabilities))) %>%
gather(key= "predictors", value="predictor.value", -logit)
```

```{r}
ggplot(wine1, aes(logit, predictor.value))+
geom_point(size=.5, alpha=.5)+
geom_smooth(method= "loess")+
theme_bw()+
facet_wrap(~predictors, scales="free_y")
```

## Assumption #5: Absence of Influential Outliers *** MODIFY TO FIT NEW ANALYSIS ***

```{r}
infl <- influence.measures(mylogit)
summary(infl)
```
### Results indicate no evidence of **influential** outliers

Box Plot Method

### all box plots
```{r}
boxplot(wine1)
ggplot(stack(wine1), aes(x = ind, y = values))+
  geom_boxplot(fill='rosybrown', color="darkred") +
  coord_flip()
```

All variables have outliers.

*********************** MOVING FORWARD **************************

# Correcting for Violation of Assumptions

## Corrections for Violation of Multicollinearity

```{r}
```

## Corrections for Violation of Logit Linearity
```{r}
```




# Creating a Base Model  

## Define the Order of the Dependent Variable
```{r}

wine_wrangled$qualityR = factor(wine_wrangled$qualityR, levels = c("0", "1", "2"), ordered = TRUE) 

```

## Dividing data into training and test set  *** REVIEW THIS SECTION ***
*** how to determine appropriate sample size
*** what is seed and how to determine appropriate value

### Random sampling 
```{r}

samplesize = 0.60*nrow(wine_wrangled)
set.seed(100)
index = sample(seq_len(nrow(wine_wrangled)), size = samplesize)

```

### Creating training and test set 
```{r}
datatrain = wine_wrangled[index,]
datatest = wine_wrangled[-index,]
```

## Create the Ordinal Logistic Regression Model
```{r}

model= polr(qualityR ~ fixed.acidity + volatile.acidity + citric.acid + residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide + density + pH + sulphates + alcohol, data = wine_wrangled, Hess = TRUE)

summary(model)

```

## Significance Table of coefficients and intercepts

```{R}
summary_table <- coef(summary(model))
pval <- pnorm(abs(summary_table[, "t value"]),lower.tail = FALSE)* 2
summary_table <- cbind(summary_table, "p value" = round(pval,3))
summary_table
```

## Explanation of Results:


# Making predictions


## Creating a Confusion Matrix *** MODIFY TO FIT NEW ANALYSIS ***

```{r}
cmatrix <- caret::confusionMatrix(wineqt$PredictedR, wineqt$qualityR2)
cmatrix
```





