---
title: "LDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Libaries
```{r}
library(MASS)
library(ggplot2)
```

Set Working Directory
```{r}
setwd("/Users/erinweaver/Documents/GitHub/TheThreeMusketeers/")
```

Import Data Set
```{r}
wine <- read.csv("/Users/erinweaver/Documents/GitHub/TheThreeMusketeers/Data/WineQT.csv")
head(wine)
```

Wrangle to Key Variables
```{r}
wine_wrangled <- wine[, c(2,5,8,9,12)]
head(wine_wrangled)
```

View Structure of Dataset
``` {r}
str(wine_wrangled)
```

Set Quality to Factor
``` {r}
wine_wrangled$quality = factor(wine_wrangled$quality, levels = c("3", "4", "5", "6", "7", "8"), ordered = TRUE)
```

View Structure of Dataset
``` {r}
str(wine_wrangled)
```

Scale each predictor variable:
```{r}
wine_wrangled[1:4] <- scale(wine_wrangled[1:4])
```

Find the mean of each predictor variable:
```{r}
apply(wine_wrangled[1:4], 2, mean)
```

Find standard deviation of each predictor variable:
```{r}
apply(wine_wrangled[1:4], 2, sd) 
```

Make this example reproducible:
```{r}
set.seed(1)
```

Use 70% of dataset as training set and remaining 30% as testing set
```{r}
sample <- sample(c(TRUE, FALSE), nrow(wine_wrangled), replace=TRUE, prob=c(0.7, 0.3))
train <- wine_wrangled[sample, ]
test <- wine_wrangled[!sample, ] 
```

Fit LDA model
```{r}
model <- lda(quality~., data=train)
```

View model output
```{r}
model
```

model$counts
model$prior
model$scaling
model$svd

Store Model Means
```{r}
modelmeans <- model$means
```

Convert Matrix to Data Frame
```{r}
modelmeans <- as.data.frame(modelmeans)
str(modelmeans)
```

Convert row labels to column
```{r}
library(tibble)
modelmeans <- tibble::rownames_to_column(modelmeans, "quality")
```

Plot Means
Melt Dataframe
```{r}
library(reshape2)
mmodelmeans <- melt(modelmeans, id.vars="quality")
```

Export Means
```{r}
write.csv(mmodelmeans,"/Users/erinweaver/Documents/GitHub/TheThreeMusketeers/Data/modelmeans.csv", row.names = FALSE)
```

Everything on the same plot
```{r}
ggplot(mmodelmeans, aes(quality, value, group=variable, col=variable)) + 
  geom_line() +
  geom_point() + 
  stat_smooth() 
```

Separate plots
```{r}
ggplot(mmodelmeans, aes(quality, value, group=variable, col=variable)) + 
  geom_point() + 
  stat_smooth() +
  facet_wrap(~variable)
```

Misclasification rate
```{r}
#lda.pred = (test$class)
#lda.error = mean(default$default != lda.pred)
#lda.error
```

Confusion matrix
```{r}
#LDA_model = lda.cm
#LDA_model
```

Use LDA model to make predictions on test data
```{r}
predicted <- predict(model, test)
```

View predicted class for first six observations in test set
```{r}
head(predicted$class)
```

View posterior probabilities for first six observations in test set
```{r}
head(predicted$posterior)
```

View linear discriminants for first six observations in test set
```{r}
head(predicted$x)
```

Find accuracy of model
```{r}
#mean(predicted$class==test$quality)
```

Define data to plot
```{r}
lda_plot <- cbind(train, predict(model)$x)
```

Create plot
```{r}
ggplot(lda_plot, aes(LD1, LD2, LD3, LD4)) +
  geom_point(aes(color = quality))
```

