---
title: "LDA - Some Outliers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load Libaries
```{r}
library(MASS)
library(ggplot2)
```
###Set Working Directory
```{r}
setwd("/Users/erinweaver/Documents/GitHub/TheThreeMusketeers/")
```

###Import Data Set
```{r}
wineqt <- read.csv("/Users/erinweaver/Documents/GitHub/TheThreeMusketeers/Data/WineQT.csv")
head(wineqt)
```

Wrangle to Key Variables
```{r}
wine_wrangled <- wineqt[, c(2,5,8,9,12)]
head(wine_wrangled)
```

View Structure of Dataset
``` {r}
str(wine_wrangled)
```

Set Quality to Ordered Factor
``` {r}
wine_wrangled$quality = factor(wine_wrangled$quality, levels = c("3", "4", "5", "6", "7", "8"), ordered = TRUE)
```

View Structure of Dataset
``` {r}
str(wine_wrangled)
```

*** STOP SIGN ***

Identify Outliers

```{r}
boxplot.stats(wine_wrangled$density)
# OUTLIER COUNT - 36
```
```{r}
boxplot.stats(wine_wrangled$chlorides)
# OUTLIER COUNT - 77
```
```{r}
boxplot.stats(wine_wrangled$volatile.acidity)
# OUTLIER COUNT - 14
```

```{r}
boxplot.stats(wine_wrangled$pH)
# OUTLIER COUNT - 20
```

REMOVE OUTLIERS (Chlorides)

```{r}
chloride.Q1 <- quantile(wine_wrangled$chlorides, .25)
chloride.Q3 <- quantile(wine_wrangled$chlorides, .75)
chloride.IQR <- IQR(wine_wrangled$chlorides)
```
```{r}
no_outliers_c <- subset(wine_wrangled, wine_wrangled$chlorides > (chloride.Q1 - 1.5*chloride.IQR) & wine_wrangled$chlorides < (chloride.Q3 + 1.5*chloride.IQR))
```

```{r}
boxplot(no_outliers_c)
```

RECHECK OUTLIER COUNT:

```{r}
boxplot.stats(no_outliers_c$pH)
# outlier count - (23)
```

```{r}
boxplot.stats(no_outliers_c$volatile.acidity)
# outlier count - (12)
```

```{r}
boxplot.stats(no_outliers_c$density)
# outlier count - (29)
```

REMOVE OUTLIERS (Density)

```{r}
density_Q1 <- quantile(no_outliers_c$density, .25)
density_Q3 <- quantile(no_outliers_c$density, .75)
density_IQR <- IQR(no_outliers_c$density)
```
```{r}
no_outliers_cd <- subset(no_outliers_c, no_outliers_c$density > (density_Q1 - 1.5*density_IQR) & no_outliers_c$density < (density_Q3 + 1.5*density_IQR))
```

```{r}
boxplot(no_outliers_cd)
```

RECOUNT OUTLIERS
```{r}
boxplot.stats(no_outliers_cd$volatile.acidity)
# outlier count - (12)
```

```{r}
boxplot.stats(no_outliers_cd$pH)
# outlier count - (17)
```

*** BUILDING THE MODEL ***

Scale each predictor variable:
```{r}
no_outliers_cd[1:4] <- scale(no_outliers_cd[1:4])
```

Find the mean of each predictor variable:
```{r}
apply(no_outliers_cd[1:4], 2, mean)
```

Find standard deviation of each predictor variable:
```{r}
apply(no_outliers_cd[1:4], 2, sd) 
```

Make this example reproducible:
```{r}
set.seed(1)
```

Use 70% of dataset as training set and remaining 30% as testing set
```{r}
sample <- sample(c(TRUE, FALSE), nrow(no_outliers_cd), replace=TRUE, prob=c(0.7,0.3))
train <- no_outliers_cd[sample, ]
test <- no_outliers_cd[!sample, ] 
```

Fit LDA model
```{r}
model <- lda(quality~., data=train)
```

View model output
```{r}
model
```

Functions to Call Specifics:
model$counts
model$prior
model$scaling
model$svd


GRAPHING MODEL MEANS

Store Model Means
```{r}
modelmeans <- model$means
```

Convert Matrix to Data Frame
```{r}
modelmeans <- as.data.frame(modelmeans)
str(modelmeans)
```

Convert row labels to column
```{r}
library(tibble)
modelmeans <- tibble::rownames_to_column(modelmeans, "quality")
```

Melt Dataframe
```{r}
library(reshape2)
mmodelmeans <- melt(modelmeans, id.vars="quality")
```

Everything on the same plot
```{r}
ggplot(mmodelmeans, aes(quality, value, group=variable, col=variable)) + 
  geom_line() +
  geom_point() + 
  stat_smooth() 
```

Separate plots
```{r}
ggplot(mmodelmeans, aes(quality, value, group=variable, col=variable)) + 
  geom_point() + 
  stat_smooth() +
  facet_wrap(~variable)
```


**** CHECKING THE MODEL QUALITY ****

###Misclasification rate
```{r}
#lda.pred = (test$class)
#lda.error = mean(default$default != lda.pred)
#lda.error
```

###Confusion matrix
```{r}
#LDA_model = lda.cm
#LDA_model
```

###Use LDA model to make predictions on test data
```{r}
predicted <- predict(model, test)
```

###View predicted class for first six observations in test set
```{r}
head(predicted$class)
```

###View posterior probabilities for first six observations in test set
```{r}
head(predicted$posterior)
```

###View linear discriminants for first six observations in test set
```{r}
head(predicted$x)
```

###Find accuracy of model
```{r}
#mean(predicted$class==test$quality)
```

###Define data to plot
```{r}
lda_plot <- cbind(train, predict(model)$x)
```

###Create plot
```{r}
ggplot(lda_plot, aes(LD1, LD2, LD3, LD4)) +
  geom_point(aes(color = quality))
```


